Manuscript Figures

### 2024-06-07 Manuscript_Figures.Rmd
New burn plot

Read in IC map and IC csv. Find tree species with highest biomass for each MapCode, then add that info to the raster.
```{r}
IC_tif <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","IC_Map_FortBragg.tif"))
IC_map <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","output-community-0.img"))
crs(IC_map) <- crs(IC_tif)
ext(IC_map) <- ext(IC_tif)

@@

```{r}
bp4 <- vect(here("BurnPlots","FB_plot4.shp")) %>%
  project(crs(IC_dom_map))
map_colors <- c(colorblind_pal()(8)[c(2,3,1,4,5,6,7,8)],"gray70")
ggplot() +
  geom_spatraster(data=IC_dom_map) +
  geom_spatvector(data=bp4, fill=NA, color = "red", linewidth = 0.75) +
  scale_fill_manual(values=map_colors, na.value = NA) +
  labs(fill="Dominant Tree Species") +
  theme_bw()
ggsave("IC_map.jpg", path=here("Plots"), width = 7, height = 3)
```

@@

Look at the dominant tree species
```{r}
bp4 <- vect(here("BurnPlots","FB_plot4.shp")) %>%
  project(crs(IC_dom_map))

ext_new = ext(bp4)
ext_new[1] = ext_new[1]-60
ext_new[2] = ext_new[2]+60
ext_new[3] = ext_new[3]-60
ext_new[4] = ext_new[4]+60
IC_crop_bp4 <- crop(IC_dom_map,ext_new)
```
```{r}
ggplot() +
  geom_spatraster(data=IC_crop_bp4)+
  scale_fill_colorblind()+
  geom_spatvector(data=bp4,fill=NA,linewidth=1)+
  theme_bw()
```

>>>>

Read in IC map and IC csv. Find tree species with highest biomass for each MapCode, then add that info to the raster.
```{r}
IC_tif <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","IC_Map_FortBragg.tif"))
IC_map <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire5-Dry","output-community-0.img"))
crs(IC_map) <- crs(IC_tif)
ext(IC_map) <- ext(IC_tif)

@@

```{r}
bp4 <- vect(here("1.LANDIS-MODEL","Shapefiles","burn_plot.shp")) %>%
  project(crs(IC_dom_map))
map_colors <- c(colorblind_pal()(8)[c(2,3,1,4,5,6,7,8)],"gray70")
ggplot() +
  geom_spatraster(data=IC_dom_map) +
  geom_spatvector(data=bp4, fill=NA, color = "red", linewidth = 0.75) +
  scale_fill_manual(values=map_colors, na.value = NA) +
  labs(fill="Dominant Tree Species") +
  theme_bw()
ggsave("IC_map.jpg", path=here("Plots"), width = 7, height = 3)
```

@@

Look at the dominant tree species
```{r}
bp4 <- vect(here("1.LANDIS-MODEL","Shapefiles","burn_plot.shp")) %>%
  project(crs(IC_dom_map))

ext_new = ext(bp4)
ext_new[1] = ext_new[1]-60
ext_new[2] = ext_new[2]+60
ext_new[3] = ext_new[3]-60
ext_new[4] = ext_new[4]+60
IC_crop_bp4 <- crop(IC_dom_map,ext_new)
```
```{r}
single_colors <- colorblind_pal()(8)[c(2,5,6)]
ggplot() +
  geom_spatraster(data=IC_crop_bp4)+
  scale_fill_manual(values = single_colors)+
  geom_spatvector(data=bp4,fill=NA,linewidth=1)+
  theme_bw()
```
